---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## What is gpx?

Very simple package which converts [GPX](https://www.topografix.com/GPX/1/1/) files to `sf` objects. 


```{r}
library(gpx)
library(sf) ## for print methods of sf objects
gpx <- system.file("gpx/city_trail.gpx", package = "gpx")
sf <- gpx::gpx_sf( gpx )

sf

```

And that's it.

However, the real benefit, and the reason I built this package, is so we can plot them in mapdeck's trip layer

```{r, eval = FALSE, echo = FALSE}
library(mapdeck)

set_token( read.dcf("~/Documents/.googleAPI",fields = "MAPBOX"))

sf <- gpxsf::gpx_sf( gpx, time = "counter" )

mapdeck(
  	style = mapdeck_style("dark")
	, location = c(145., -37.8)
	, zoom = 10
) %>% 
  add_trips(
    data = sf
  )

```

## How are timestamps handled?

The timestamp can specified as one of

- datetime (default) - the numeric representation of POSIX dates
- counter - every track starts from 0 and counts to the maximum time
- normalise - every track's time is rescaled to be [0,1]

Here are some examples

```{r}

sf_time <- gpx_sf( gpx, time = "datetime" )
sf_count <- gpx_sf( gpx, time = "counter" )
sf_norm <- gpx_sf( gpx, time = "normalise" )

d <- getOption("digits")
options(digits = 12)

track_time <- unclass( sf_time[, "geometry"][[1]][[1]] )
head( track_time )

summary( track_time[, 4] )

track_count <- unclass( sf_count[, "geometry"][[1]][[1]] )
head( track_count )

summary( track_count[, 4] )

track_norm <- unclass( sf_norm[, "geometry"][[1]][[1]] )
head( track_norm )

summary( track_norm[, 4] )

options(digits = d)
```

### Surely there's something else?

Oh yes, it's quite quick too!

This example compares reading 364 gpx files using this library, compared to reading a single gpx file using `library(plotKML)`

```{r, eval = FALSE}

library(plotKML)
library(microbenchmark)

fp <- path.expand("../../Data/Strava/Bethan/activities/")
fp <- path.expand("~/Downloads/activities/")
l <- list.files(fp, patter = "gpx$")

gpx <- paste0(fp, l)

length( gpx )
# 364

sf <- gpx::gpx_sf( gpx, time = "counter" )

mapdeck(
  	style = mapdeck_style("dark")
	#, location = c(145., -37.8)
	, zoom = 10
) %>%
  add_trips(
    data = sf
    , trail_length = 4000
    , animation_speed = 800
    , stroke_width = 25
    , stroke_colour = "#FDE725BB"
  )


microbenchmark::microbenchmark(
  gpx = {
    sf <- gpx::gpx_sf( gpx )
  },
  kml = {
    #kml <- plotKML::readGPX( gpx[2]( )
    lst <- lapply( gpx[1:5], plotKML::readGPX )
  },
  times = 1
)

# Unit: seconds
#  expr      min       lq     mean   median       uq      max neval
#   gpx 3.486148 3.486148 3.486148 3.486148 3.486148 3.486148     1
#   kml 3.926912 3.926912 3.926912 3.926912 3.926912 3.926912     1

```

